Learning Actionable Analytics (with applications for reducing defects and reducing runtimes)

### 2015-05-10 how.tex
Updates from ShareLaTeX

 \documentclass[conference]{IEEEtran}
\usepackage{subfig}
\usepackage{wrapfig}
 \usepackage{amsmath}
 \usepackage{url}
 \usepackage{pifont}
 %\usepackage{times}
\usepackage{rotating}
%\usepackage{balance} 
\usepackage{color, colortbl}
\usepackage{graphicx}
\usepackage{algorithmicx}
\usepackage[running]{lineno}
\usepackage{program}
\usepackage{cite}
\usepackage{alltt}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\textsection\ref{sec:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\definecolor{lightgray}{gray}{0.975}
\usepackage{fancyvrb}
\usepackage{stfloats}
\usepackage{multirow}
\usepackage{listings}
\usepackage{amsmath}  
\DeclareMathOperator*{\argmin}{arg\,min} 
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\title{Learning Actionable Analytics 
 (with applications for reducing defects and reducing runtimes)}
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
Rahul Krishna, Tim Menzies, Xipeng Shen\\
       \affaddr{Computer Science, NcState, USA}\\
       \{i.m.ralk, tim.menzies, xipengshen\}@gmail.com
% 3rd. author
 % use '\and' if you need 'another row' of author names
% 4th. author
\and
 Andrian Marcus\\
       \affaddr{Computer Science, UtDallas, USA}\\
       {amarcus@utdallas.edu} }

@@

Later in that discussion, another business user asked:
\begin{quote}
ISSUE~\#2: {\em ``But what if I do not have a domain model of my business?''}
\end{quote}
This also is a legitimate issue.
Building and certifying a model  can  takes  long time, especially in software engineering. For  example, in previous work~\cite{me07f} we used models
developed by Boehm's group at the University of Southern California.
Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}). 
Also, even when there is an existing model, they can require
constant  maintenance lest they become out-dated. Elsewhere, we have described our
extensions to the USC models to enable reasoning about agile software developments. 
It took many months to implement and certify those extensions~\cite{me09i,me09j}.
The problem of model maintenance is another
motivation to look for alternate methods that can be automatically updated whenever new data arrives.
Further, sometimes  it is easier to access instances of a model's behaviour than the model
itself. For example, in prior work with Martin  Feather from the Jet Propulsion 
Laboratory~\cite{fea02a},  our research partner could not share a
propriety model from within the NASA firewalls. However, they could share 
logs of the input/output of that model.

@@

@@

\input{code}

Those same regions can be used for instance-based 
{\em planning}-- but instead of leaving test instances in the regions
found during training, we {\em displace} them towards regions
with better objective scores.
To achieve this, 
during training, HOW clusters data using the procedure of \fig{where}a,
then draws {\tt Line}s between the centroids of  clusters $X,Y$ that are nearest
neighbors.
By convention, we say that the cluster containing $X$ has the  better objective scores. This means we can say that the {\tt Line} is a useful direction for displacing
data; i.e.  away from $Y$ and towards $X$ (for an implementation of such a {\tt Line} class, see \fig{howcode}, line~1).
 During testing,  HOW   finds the  nearest {\tt Line} to every test instance. That  test instance is   then displaced towards the better end
of that line; i.e. towards  $X$ (see \fig{howcode}, line 53).

>>>>

\documentclass[conference]{IEEEtran}
%related work (gentling them in)
%future work: local patch operator
%complexity
% planning in ai

\usepackage{subfig}
\usepackage{wrapfig}
 \usepackage{amsmath}
 \usepackage{url}
 \usepackage{pifont}
 %\usepackage{times}
\usepackage{rotating}
%\usepackage{balance} 
\usepackage{color, colortbl}
\usepackage{graphicx}
\usepackage{algorithmicx}
\usepackage[running]{lineno}
\usepackage{program}
\usepackage{cite}
\usepackage{alltt}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\textsection\ref{sec:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\definecolor{lightgray}{gray}{0.975}
\usepackage{fancyvrb}
\usepackage{stfloats}
\usepackage{multirow}
\usepackage{listings}
\usepackage{amsmath}  
\DeclareMathOperator*{\argmin}{arg\,min} 
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\title{Learning Actionable Analytics 
 (with applications for reducing defects and reducing runtimes)}
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
Rahul Krishna, Tim Menzies, Xipeng Shen\\
        Computer Science, NcState, USA\\
       \{i.m.ralk, tim.menzies, xipengshen\}\@gmail.com
% 3rd. author
 % use '\and' if you need 'another row' of author names
% 4th. author
\and
 Andrian Marcus\\
       Computer Science, UtDallas, USA \\
       amarcus\@utdallas.edu }

@@

Later in that discussion, another business user asked:
\begin{quote}
ISSUE~\#2: {\em ``But what if I do not have a domain model of my business?''}
\end{quote}
This also is a legitimate issue.
As discussed below,
building (or accessing) and certifying and maintaining a 
trust-worthy model  can  takes  long time, especially in software engineering.

@@

\section{Related Work}
\subsection{Accessing a Trustworthy model}
The premise of this work is that we do {\em not} have
a ready-to-use

In some domains, there is ready access to 
trustworthy domain model that can offer an assessment
of newly generated examples. For example, in other work
we have used executing source code as the ``model'' to check
if our mutations to test suites
  minimize
test suite size while maximizing the number of statements covered~\cite{}

For  example, in previous work~\cite{me07f} we used models
developed by Boehm's group at the University of Southern California.
Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}). 
Also, even when there is an existing model, they can require
constant  maintenance lest they become out-dated. Elsewhere, we have described our
extensions to the USC models to enable reasoning about agile software developments. 
It took many months to implement and certify those extensions~\cite{me09i,me09j}.
The problem of model maintenance is another
motivation to look for alternate methods that can be automatically updated whenever new data arrives.
Further, sometimes  it is easier to access instances of a model's behaviour than the model
itself. For example, in prior work with Martin  Feather from the Jet Propulsion 
Laboratory~\cite{fea02a},  our research partner could not share a
propriety model from within the NASA firewalls. However, they could share 
logs of the input/output of that model.

@@

\input{_tex/code}

Those same regions can be used for instance-based 
{\em planning}. However,  instead of leaving test instances in the regions
found during training, we {\em displace} them towards regions
with better objective scores.
To achieve this, 
during training, HOW clusters data using the procedure of \fig{where}a,
then draws {\tt Line}s between the centroids of  clusters $X,Y$ that are nearest
neighbors.
By convention, we say that the cluster containing $X$ has the  better objective scores. This means we can say that the {\tt Line} is a useful direction for displacing
data; i.e.  away from $Y$ and towards $X$ (for an implementation of such a {\tt Line} class, see \fig{howcode}, line~1).
 During testing,  HOW   finds the  nearest {\tt Line} to every test instance. That  test instance is   then displaced towards the better end
of that line; i.e. towards  $X$ (see \fig{howcode}, line 53).
